\cvsection{Experience}

\begin{cventries}

\cventry
    {Cyber Security Engineer} % Job title
    {Solarisbank AG, Germany} % Organization
    {Berlin, Germany} % Location
    {Dec 2020 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented AWS web application firewall (WAF) for the organization applications and API endpoints.
        \item Using Terraform for day to day activities for privisioning the infrastructure and managing the resource such as AWS WAF. Implemented rules for combating OWASP Top 10, rate limiting, DoS attacks, etc. for the traffic reaching origin servers.}
        \item {Implemented endpoint security for protecting organization's assets: implemented Airwatch configuration for Mac and Windows laptops to secure against data leakage, uncontrolled usage, harmful softwares, etc.}
        \item {Application security testing (vapt) - recon and black box testing of applications and API's.}
        \item {Infrastructure penetration testing and red teaming activities  - recon and black box testing of subdomains.}
        \item {Responding to security incidents in the organization - active involvement with investigation and working on controls to be made effective.}
        \item {Leading alignment calls for cross-functional teams.}
        \item {Running awareness program to improve security across teams.}
        \item {Tech stack: AWS WAF, Cloudtrail, Cloudwatch, Athena, Config, DAST, Terraform, Airwatch}
      \end{cvitems}
    }

  \cventry
    {Security Engineer} % Job title
    {Paytm, One97 Communications Ltd} % Organization
    {Noida, India} % Location
    {July 2019 - Nov 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented static code analysis (SCA/SAST) for critical apps - implemented Sonarqube, Jenkins and Github setup for the entire organisation and tested the code for security issues.}
        \item {Implementing container security for Docker \& Kubernetes environments - implemented Prisma, Docker-bench, Clair and ECR as an image scanning and pod security tool.}
        \item {Periodically performing application security testing (vapt) - recon, black box and white box activities done on all applications of Paytm.}
        \item {Infrastructure penetration testing and red teaming activities - recon, black and white box activities done for servers.}
        \item {Maintaining Akamai web application firewall (WAF) for critical endpoints - implementing rules and active on-calls for security attacks.}
        \item {Implemented continuous security with DevOps CI/CD pipelines - developed pipeline for SAST setup.}
        \item {Managing bug bounty program i.e. bugbounty.paytm.com - report triaging, reviewing and RCAs.}
        \item {Holding workshops for source code analysis and container security.}
        \item {Tech stack: SAST, DAST, IAM, AWS, VAPT, Incident response}
      \end{cvitems}
    }

  \cventry
    {Cyber Security Engineer} % Job title
    {Ernst and Young (EY)} % Organization
    {New Delhi, India} % Location
    {June 2018 - July 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Web application security testing (vapt).}
        \item {API reviews for security vulnerabilities.}
        \item {Red Teaming activities.}
        \item {MBSS review and assessment.}
        \item {Performed source code analysis to identify security issues.}
        \item {RBI PPI and UPI technical security audit.}
      \end{cvitems}
    }

  \cventry
    {Cyber Security Researcher} % Job title
    {Researcher and Bug Bounty Hunter} % Organization
    {Various} % Location
    {Since 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Bug bounty hunter at 'Synack Red Team'.}
        \item {Latest Hall of Fame: Nykaa (High severity issue) - https://www.nykaa.com/responsible-disclosure.}
        \item {Hall of fame received from Postmates, Pepsico, Ebay, Myntra, Sakura Japan, Zomato, etc.}
      \end{cvitems}
    }

\end{cventries}
